---
title: "Introduction to Bioconductor Notes"
author: Renji
Date: "May 31, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Molecular Basis for Phenotypic Variation
• Phenotypic variation depends on differences in the DNA and also on differences in which parts of the DNA are expressed as proteins.
• We use genomic technologies to measure differences in DNA and gene expression, such as changes in the sequence or amounts of expression, and relate those changes to phenotypic variation.

# DNA: chromosomes, replication, SNPs and other variants
• Single Nucleotide Polymorphism (SNP): a single base in the genome that often differs between individuals and may cause phenotypic differences. #个体间通常非一致的单碱基位点，并且造成表型变化
• Genome-wide association studies (GWAS) are a major tool of genetic epidemiologists. 
```{r}
library(GenomicRanges)
library(gwascat)
data(ebicat37)
ebicat37
```

```{r number of GWAS hits on each chromosome}
sort(table(ebicat37$CHR_ID),decreasing=TRUE)
```

```{r access the names of diseases with genetic associations }
mcols(ebicat37)[,"DISEASE/TRAIT"]
```

# Molecular biology concepts
• There are varies RNA copies of a given gene. 
Reason: The number of copies of RNA depends on how much the gene is being transcribed. “Housekeeping genes” such as those used to make ribosomal or transfer RNA are transcribed at a high rate, while others, such as mRNA for some transcription factors, are transcribed less frequently. Some genes are not transcribed at all in certain cell types.

# Microarray technology
• Gene expression microarrays: More copies of a gene in a sample results in higher fluorescence intensity at the corresponding probe.
• The raw values that come out of a gene expression microarray experiment: the hybridization of RNA or cDNA to probes
• Example of applications: classifying tumor samples from various patients into distinct phenotypic classes